Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-14 prop_letter.tex
questions

@@

%%%
\subsection{Kochen-Specker}

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
We will use the essential idea of the Kochen-Specker theorem to prove
there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
then we have 
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kochen-Specker}

Our first result is that a QIVPM cannot be crypto-deterministic. We
will use the proof of the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}
to show that it is, in general, impossible to just have the two
intervals \imposs\ and \necess: every QIVPM must be parameterized by a
collection of intervals that includes at least one ``fuzzy'' interval
and some events must be associated with these uncertain intervals.

We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin square''
observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}

\newpage

Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
then we have 
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.

@@

% %%%
% \subsection{Kochen-Specker}

% While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
% IVPMs, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
% is another one, corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}.
% We will use the essential idea of the Kochen-Specker theorem to prove
% there is no quantum IVPM mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
% Suppose there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$.
% We can prove $\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
% where $\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
% multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
% and $\left\{ \lambda_{2}\right\} $ to be $\left\{ \lambda_{1}\lambda_{2}\right\} $,
% then we have 
% \begin{equation}
% \prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
% \end{equation}
% for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.

% Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$ satisfying
% these two properties, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
% \begin{equation}
% \begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
% \sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
% \sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
% \end{aligned}
% \label{eq:MerminSquare}
% \end{equation}
% must have the the expectation value~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
% In each row and column, operators commutes, and each operator is the
% product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
% Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
% that 
% \begin{equation}
% \begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
% \langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
% \langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
% \end{aligned}
% \label{eq:MerminSquare-values}
% \end{equation}
% satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
